Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-03-03 demystify.tex
updates

Here are some general advice to find professor.  Assuming you're not familiar with any particular one, then first, search for profs. that share similar research interests. You can learn about faculty and their level of research activity through the faculty's website or even from CSRankings.  For example, in CSRankings, if you want to work with PL, you can search for those publish in PL conferences.  If you want to work with SE \emph{and} AI, you can search for faculty who work in both SE and AI.  Then you do research about that professor and contact them (\autoref{sec:contact}).

@@

\section{Buying Computer Equipment}\label{sec:buying-equipment} Many students, including myself, get very excited about getting to buy new computer equipment and electronics when they start their PhD. However, you should check with your adviser first.  Many profs. have funding to buy you a computer and other equipments (e.g., keyboards, headphones, tablets, etc).  Also, do not worry that this is a "waste" of your adviser's money.  This is part of the funding that your adviser gets to support you and your research.  So use it to get what you need to do your research (and it's also OK to use them for personal purposes!).

>>>>

Here are some general advice to find professor.  Assuming you're not familiar with any particular one, then first, search for profs. that share similar research interests.  For example, in CSRankings, if you want to work with PL, you can search for those publish in PL conferences.  If you want to work with SE \emph{and} AI, you can search for faculty who work in both SE and AI.  Then you do research about that professor and contact them (\autoref{sec:contact}).

@@

\section{Buying Computer Equipment}\label{sec:buying-equipment} Many students, including myself, get very excited about getting to buy new computer equipment and electronics when they start their PhD. However, you should check with your adviser first.  Many profs. have funding to buy you a computer and other equipments (e.g., keyboards, headphones, tablets, books, etc).

\section{Can I negotiate my PhD offer?}\label{sec:negotiate}
For stipend, unlikely. TA is set by the university and while RA is set by the adviser, it is often based on the department's standard and it would be unfair to other students if you get more.  For start date or TA assignment (e.g., TA a specific course), it is uncommon but you can ask for it. Also, there is typically no moving allowance for PhD students. In short, things that are standard and set by the university or department are unlikely to be negotiable.  However, you can ask for things such as computer equipments (\autoref{sec:buying-equipment}), books, (and sometimes even furniture) and conference travel budget.
